Thesis Draft

### 2015-10-21 chapter2.tex
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d

\chapter{Theory of Trash}
In this chapter trash is examined in theoretical (and conceptual) aspect. Theoretical foundations of trash are discussed. (Further benefited from historical and social aspect of trash.)

%%%
%%%
%%%
\section{Etymology}
(Garbage, trash, rubbish, debris, detritus, waste: during my research scholars and authors all have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash. There are slight differences between these words but sometimes they are used to signify same concept.

%%
%%
\subsection{Origins of words: waste, trash, rubbish, scrap, junk, refuse, discard, litter}
The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?

@@

%%
%%
\subsection{The difference between reuse and recycle}
According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. If any item is used again and again over time, it is said to be reused. The main purpose of reusing is to lengthen the life of the item or material. We give out used clothes for charity which results in reusing. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. Why throw something away when you can give it another life? Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

@@

According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product. It is an energy consuming process. For example, if we put some plastic bottles, paper, or aluminium items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt. In this process, energy is required which depends upon the stages of transformation.

@@

@@

@@

>>>>

\chapter{Theory of Trash}

% FROM Uncle Fernando’s Garbage Triptych, http://alphabet-city.org/issues/trash/articles/uncle-fernando-s-garbage-triptych
\epigraph{\textit{\quotes{Anger is nothing compared to garbage:\\ Garbage eats anger for breakfast.\\ It eats all of us in the end.}}}{\hfill --- Priscilla Uppal}

In this chapter trash is examined in theoretical (and conceptual) aspect. Theoretical foundations of trash are discussed. (Further benefited from historical and social aspect of trash.) How do scholars conceptualized the trash? What do they say about it? In this chapter it will presented. It draws attention of many scholars and people who are professional in different areas. Further trash is a topic that common for the all ages through the human history. In other word this topic is not a new one. It always part of the human practice. It can be thought that it is refused, discarded thing as soon as possible there are people also carefully observing the concept giving attention to the discarding things.

%%%
%%%
%%%
\section{Etymology/Terminology}
(Garbage, trash, rubbish, debris, detritus, waste, scrap, junk, refuse, discard, disposal, litter: during my research scholars and authors all have different names for the stuff.) I realized that many scholars and resources have used different words (or terminology) to define trash. Although there are slight differences between these words, sometimes they are used to signify same concept. It is important to understand vocabulary of this topic before dive into the theory. It is very important to choose right terminology, because ... and also make more clearer the border of the work. As mentioned it very diverse vocabulary to define the practice and there is no agreed terminology. Some scholars uses junk art, other recycling art. Sometimes it makes difficult to research on this topic. And also I must point out that this topic is not limited with the English language. The topic is broad and it is not limited with english literature and vocabulary. 
% TODO reference for other languages and societies.

%%
%%
\subsection{Origins of Words}
The origin of these synonyms reveals a whole side of human activity: our history revealed by what we have thrown away through the ages. What were people throwing out when these words were coined?

@@

%%
%%
\subsection{Reuse and Recycle}
One of the most encountered words in this topic (transforming trash) is reuse and recycle. Both of them are used to signify the concept.

According to the dictionary, the word “reuse” means “to employ for some purpose” or “to put into service.” Reusing involves usage of the same product unchanged in form. If any item is used again and again over time, it is said to be reused. The main purpose of reusing is to lengthen the life of the item or material. We give out used clothes for charity which results in reusing. Other examples are; buying some items and then selling them as used items, repairing some lawn equipment and reusing them, upgrading a computer, renting books, journals, periodicals, DVDs and others. The main purpose is to make the item last as long as it can. To reuse is to use something again instead of throwing it away or sending it off to a recycling company. Why throw something away when you can give it another life? Reusing is the second best way to conserve and be earth-friendly because it keeps items out of landfills and reduces the greenhouse emissions caused by purchasing a new product. Using something multiple times -- like using a disposable container more than once -- is not the only way to reuse; you can also give old items a new purpose. For example, use an empty coffee can to store small craft supplies or an old loofah as a scouring sponge for cleaning sinks.

@@

According to the dictionary, “recycle” means “to treat or process (used or waste materials) so as to make suitable for reuse.” In recycling an item, it is processed into a totally new product. It is an energy consuming process. For example, if we put some plastic bottles, paper, or aluminum items in a recycling bin, these materials may be recycled into a totally different thing as clothing items, fabric, or maybe a quilt. In this process, energy is required which depends upon the stages of transformation.

@@

% Here is important thing is moving nature of trash. Objects moves and gains different meanings through this movement. Sometimes it becomes artwork, sometimes it becomes archelogical part, waits in the dumpsite or wait to be recycle. It also signifies that it is relative and result of a classification issue. All of them are creates a harmony. supports each other with different words and conceptualization.

@@

%%% Reference from Identity, mobility and the throwaway society
we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
\quotes{In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society. In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new. Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act. The thesis, however, lacks depth and provenance. It is, actually, glib. Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.}
% In this paper criticized the perception of throw away culture and arguments. They show the weak points of the arguments. What I understand from trow away culture?

@@

%%% Reference
% we live in a throwaway society (Barr, 2004; Cooper, 2003, 2005; Cooper and Mayers, 2000; Strasser, 1999, cf. O’Brien, 1999; Hawkins and Muecke, 2003); 
% In the two previous sections we have demonstrated the paucity of the thesis of the throwaway society. In this thesis the undeniable matter of waste, itself pressing, urgent and excessive, is used to infer the presence of a society defined by its generation; a society ceaselessly discarding and abandoning its surplus as excess, as part of an endless desire for the new. Morally corrupt and unequivocally environmentally damaging, the rhetoric of the throwaway society classifies discarding as intrinsically bad and commands us to assume control of our wasting, suggesting the adoption of heightened regulatory practices around disposal as the means to ensure that we clean-up our act. The thesis, however, lacks depth and provenance. It is, actually, glib. Indeed, to infer the presence of a throwaway society from contemporary levels of waste generation is problematic for at least four reasons.

\section{Summary}
What can be extracted from all these words?

\begin{itemize}
\item Shared practice through the different ages of humanity and different societies. 
\item Moving nature of trash.
\item Classification, not the related with the object property. 
\item Value creation, shifts in the society. 
\end{itemize}

Thompson thinks that the switch only occurs from losing all the value given the object. He refers that to gain new value previous systems ruins must be cleaned. Changing the context by first rubbishing them.

### 2015-10-21 chapter3.tex
proof reading
Former-commit-id: 7c220d1d1fb1e8bf9dd8f0cfb079c5d5b267d94d

\chapter{Trash as Medium (Trash in the Art)}
How does trash draw attention of artist(, and also mine)? In this chapter how artist approached to the trash and their techniques are discussed in the context of art. (Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?). How does it turn to medium?

@@

@@

%junkyard art

@@

% Phrases...
% What specific social issues are you trying to address through Labyrinth?

>>>>

\chapter{Trash as Medium (Trash in the Art)}

\epigraph{\textit{\quotes{One day, in a rubbish heap, I found an old bicycle seat lying beside a rusted handlebar, and my mind instantly linked them together. I assembled these two objects, which everyone then recognized as a bull’s head. The metamorphosis was accomplished, and I wish another metamorphosis would occur in the reverse sense. If my bull’s head were thrown in a junk heap, perhaps one day some boy would say, \singlequotes{Here’s something that would make a good handlebar for my bicycle!} }}}{\hfill ---Pablo Picasso}

How does trash draw attention of artist(, and also mine)? In this chapter how artist approached to the trash and their techniques are discussed in the context of art. (Historical development, methodologies, tactics, motivations\ldots) Focused on visual (plastic) arts(, because there is also a music genre called as trash music?). How does it turn to medium?

@@

\item Nelson’s breakthrough work was The Coral Reef, which he mounted in 2000 at Matt’s Gallery from objects and debris gathered from alleys, trash bins, and car-trunk sales all over London. The title refers to Nelson’s aim of creating an intricate, reeflike network of lives “all existing under one sea, which is capitalism,” he says. (It is very corralate between Ages Varda's work. She shows at the side of human practice, Nelson looks the topic from object side.)

@@

% junkyard art

@@

%*************************************
% Phrases...
% What specific social issues are you trying to address through Labyrinth?
% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art. Table 1 organizes this classification according to a set of multiple criteria. (But this one can be used at introduction, but it is too long to fit on introduction. Maybe select works by giving prominence to some of the features. So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art. Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.) 
\section{Crowdsourcing, Participation}
% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}. The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers. Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing. Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.

The value of crowdsourcing lies in the collective intelligence of the contributors. Pierre Levy (1997) describes this concept as “a form of universally distributed intelligence, constantly enhanced, coordinated in real time, and resulting in the effective mobilization of skills” (p. 13). The question of collective intelligence—and its potential efficiency in various practical settings—has received much attention in both academia and journalism. Researchers studying team performance generally agree that, under the right circumstances and with appropriate motivation, large groups of people can work together and harness their collective intelligence to achieve efficient results (Benkler, 2006; Rheingold, 2002; Surowiecki, 2004). Nevertheless, artistic creativity is different from innovation and intelligence, and it requires a unique set of skills and sensibilities as well as a particular type of cultural capital; if we admit that crowds can have collective intelligence, do they also have collective creativity in an artistic sense?

All these pages are rescued and with their [hi]story they are separated from unused new produced blank sheets and notebooks. They are not bought, not gift. They are found. They are accepted. One of the most creative medium is paper and pencil. Chance given to the people through this work.

However, in view of its reliance on the artistic contribution of a large pool of usually anonymous participants, this type of art raises important questions about notions of collective creativity, authorship, collaboration, and the shifting structure of artistic production in the new digital environment. It is well studied area. Pick a method here. Transforming trash with collaboration.

As curator Andrea Grover notes, “having the audience become co-creators is not a new impulse”; the Internet simply offered a new platform to accomplish this goal (Strickland, 2011, para. 5).

Here this question can be raised about why this type collaboration. Another option can be working together with people on a table. Creating things at that time and transforming the objects here. Possibly the connection to the people will more realistic and intense. However same things can be succeed on the internet at some level.

While crowdsourced art challenges the traditional role of the artist, it simultaneously redefines the conventional function of the public, turning them from passive receivers into engaged producers. (This totally a new area to discuss, I'm going to summarize and introduce concepts and debates. How are they support my work and how they are give way to me?)

% This article therefore aims to fill these critical gaps by analyzing the practice of online crowdsourced art within a framework of collective creativity and participation theories. Principally, my interest is in answering two key questions. What is crowdsourced art and how can it be classified? And how does the structure of the artwork determine the degree or significance of participation?

% discussion is not collaboration, collaboration is used.

% Umberto Eco's Open Work

% SketchBook Project. Inspires me a lot. Lots of works from all over the world. Full of creativity and showcase of richness of people's expressions on the small notebooks. My work can be considered as a sketch book project through trash. Sketches or only creative progress is not the only consideration. You can send your lecture notes.

% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. 
% Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

% In this thesis project case the issue is not the nature of art and its methods.
